Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-15 paper/paper.tex
Grammar issue

%We define the algorithm \TAlg in the following way.
Now we describe the algorithm \TAlg.
\TAlg partition nodes into components, and
intially each node belongs to its own singleton component.
For each pair of nodes \TAlg maintains a counter, initiated to $0$. 
Upon receiving a request to a pair that is not collocated at one server, it increases the counter by $1$.
If the counter for a pair $(u,v)$ reaches $\alpha$, \TAlg merges the components of $u$ and $v$, and moves to the closest partition, in which each component has all of its nodes collocated in one server.
If no such partition exists, \TAlg resets all components to singletons and all counters to $0$ and ends the phase.

>>>>

%We define the algorithm \TAlg in the following way.
Now we describe the algorithm \TAlg.
\TAlg partition nodes into components, and
intially each node belongs to its own singleton component.
For each pair of nodes \TAlg maintains a counter, initiated to $0$. 
Upon receiving a request to a pair that is not collocated at one server, it increases their counter by $1$.
If the counter for a pair $(u,v)$ reaches $\alpha$, \TAlg merges the components of $u$ and $v$, and moves to the closest partition where each component has all of its nodes collocated in one server.
If no such partition exists, \TAlg resets all components to singletons, resets all counters to $0$, and ends the phase.
